MultiDataProcessPico

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Removed annotation that does not apply

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20230210_PICO_MCMIX006_RUN108_TargetDataMetaFilter.Rds"

@@

Remove extraneous columns from ProcessData; could have been done at end of MultiDataImport.Rmd

>>>>

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"

@@
